Microbial interactions as drivers of a nitrifying ecosystem in a chemostat

### 2020-03-26 tex/Article_Interactions.tex
adding tex and pdf files

 The case study 2 is based on Dumont \textit{et al.}\cite{Dumont2016} model parameters. Again for studying the model behaviour a modification of the original interaction matrix is performed. They proposed a distribution of parameters obtained from a Bayesian estimation method. Their fit describes well the dynamics of the two most abundant OTU in each functional group, but it still fails to capture the measured substrates dynamics. Kinetic parameters of case study 2 can be seen in table \ref{kinetic_parameters}. The original interaction matrix estimated by them is seen in \ref{Interaction_1}. A second matrix is presented, which is obtained from modification on the sign of coefficient $a_{11}$ as seen in \ref{Interaction_2}, and finally a third one is obtained by changing the value of $a_{12}$ from the original matrix.

@@

The approach was tested against synthetic data. The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2}. Therefore in the former framework the interaction function is $I(x) = 1 + Ax$, $f_i(s) = \dfrac{s_1}{K_i +s_1}$ for $i \in G_1$, and $f_i(s) = \dfrac{s_2}{K_i +s_2}$ for $i \in G_2$, for $n_1 = 10$ and $n_2 = 5$, with a randomly generated matrix $A$ in figure \ref{Interaction Matrix Simulation}. Parameters of the simulation can be seen in table.  The simulated synthetic OTU trajectories can be seen in figures \ref{fig:nonoise200121aobplot} and \ref{fig:nonoise200121nobplot}, and the metabolites can be seen in figure \ref{fig:nonoise200121metabolites}.

The operating and ecological diagrams are shown in figure.

\begin{table}[ht]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $k_i =\frac{1}{y_i} \, [gr/gr]$ \\ \hline
		$x_i \in G_1$ &0.77  &0.7  & 3.94 \\ \hline
		$x_i\in G_2$ & 0.621 & 1.3 & 16.12 \\ \hline
	\end{tabular}
	\caption{Kinetic parameters of model \eqref{system} modified from \cite{Dumont2016}.}
	\label{Parameters_synthetic_data}
\end{table}

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45 \linewidth}
	\includegraphics[width=\linewidth]{proof_of_concept/no_noise_200121_AOB_plot}
	\caption{}
	\label{fig:nonoise200121aobplot}
	\end{subfigure}
	\begin{subfigure}{0.45 \linewidth}
	\centering
	\includegraphics[width=\linewidth]{proof_of_concept/no_noise_200121_NOB_plot}
	\caption{}
	\label{fig:nonoise200121nobplot}
	\end{subfigure}
\caption{}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{proof_of_concept/no_noise_200121_metabolites}
	\caption{}
	\label{fig:nonoise200121metabolites}
\end{figure}

\begin{figure}[h]
	\centering	
	\begin{subfigure}{0.45 \linewidth}
		\includegraphics[width=\linewidth]{Synthetic_data_no_noise/Interactions_synthetic_data_no_noise}
		\caption{Interaction matrix associated with model \eqref{system} for a simulated consortia of 15 bacterial species where $x_1$-$x_{10}$ are AOB and $x_{11}$-$x_{15}$ are NOB.}
		\label{Interaction Matrix Simulation}
	\end{subfigure}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Biomass_Iter_10}
	\caption{Dotted line: simulated total biomass for model \eqref{system} with interactions shown in Figure \ref{Interaction Matrix Simulation} and parameters\iffalse quels paramètres ?\fi. Continuous line: total biomass as predicted  by the tracking procedure.}
	\label{Total Biomass no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_AOB_Iter_10}
	\caption{Dotted line: simulated AOB biomass. Continuous line: the tracking procedure results.}
	\label{AOB no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_NOB_Iter_10}
	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{NOB no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_metabolites_Iter_10}
	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{Metabolites no noise}
\end{figure}
\clearpage

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Control_AOB_Iter_10}
	\caption{Control for the AOB population.}
	\label{Control AOB no noise}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Control_NOB_Iter_10}
	\caption{Control for the NOB population.}
	\label{Control NOB no noise}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//Comparison_different_control}
	\caption{Obtained controled for different $\lambda$ for two OTU and the interaction function used in the simulation of synthetic data.}
	\label{Comparison_lambda}
\end{figure}

>>>>

 The case study 2 is based on Dumont \textit{et al.}\cite{Dumont2016} model parameters. They proposed a distribution of parameters obtained from a Bayesian estimation method. Their fit describes well the dynamics of the two most abundant OTU in each functional group, but it still fails to capture the measured substrates dynamics. Kinetic parameters of case study 2 can be seen in table \ref{kinetic_parameters}. The original interaction matrix estimated by them is seen in \ref{Interaction_1}. A second matrix is presented, which is obtained from modification on the sign of coefficient $a_{11}$ as seen in \ref{Interaction_2}, and finally a third one is obtained by changing the value of $a_{12}$ from the original matrix.

@@

The approach was tested against synthetic data generated by simulating model \eqref{system} using the parameters of the study case 1 with interaction matrix given by \eqref{case1_interactions}. In the operating diagram of the same case (figure \eqref{OD_interactions}) the red zone implies complete nitrification, while the green zone means partial nitrification. For integrating the former phenomena in the simulation, the system was simulated for 300 days, and perturbed at day 150 from the CN zone ($(s_{in},D) = (1.25,0.22)$) to a PN zone ($(s_{in},D) = (1.95,0.22)$) .

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45 \linewidth}
	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_AOB_plot}
	\caption{}
	\label{fig:nonoise200121aobplot}
	\end{subfigure}
	\begin{subfigure}{0.45 \linewidth}
	\centering
	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_NOB_plot}
	\caption{}
	\label{fig:nonoise200121nobplot}
	\end{subfigure}
\caption{}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{proof_of_concept/250309_POC_metabolites}
	\caption{}
	\label{fig:nonoise200121metabolites}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_Biomass_iter_2}
	\caption{Dotted line: simulated total biomass for model \eqref{system} \iffalse quels paramètres ?\fi. Continuous line: total biomass as predicted  by the tracking procedure.}
	\label{Total Biomass no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_AOB_iter_2_plot_1}
	\caption{Dotted line: simulated AOB biomass. Continuous line: the tracking procedure results.}
	\label{AOB no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_NOB_iter_2_plot_1}
	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{NOB no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_metabolites_iter_2}
	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{Metabolites no noise}
\end{figure}
\clearpage

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45 \linewidth}
		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_Control_AOB_iter_2_plot_1}
	\caption{Control for the AOB population.}
	\label{Control AOB no noise}
	\end{subfigure}
	\begin{subfigure}{0.45 \linewidth}
		\centering
		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_Control_NOB_iter_2_plot_1}
	\caption{Control for the NOB population.}
	\label{Control NOB no noise}
	\end{subfigure}
	\caption{}
\end{figure}
\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45 \linewidth}
		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_growth_AOB_iter_2_plot_1}
		\caption{Growth rate of the model for AOB community.}
		\label{AOB_growth_POC}
	\end{subfigure}
	\begin{subfigure}{0.45 \linewidth}
		\centering
		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_growth_NOB_iter_2_plot_1}
	\caption{Growth rate of the model for the NOV community.}
	\label{NOB_growth_POC}
	\end{subfigure}
	\caption{}
\end{figure}

@@

%\begin{figure}[h]
%	\centering
%	\includegraphics[width=0.5\textwidth]{Synthetic_data//Comparison_different_control}
%	\caption{Obtained controled for different $\lambda$ for two OTU and the interaction function used in the simulation of synthetic data.}
%	\label{Comparison_lambda}
%\end{figure}
